\section{Background}
\label{sec:background}

\subsection{LLM GUI Agents and Mobile Automation Fraud}
\label{sec:bg_agents}

An LLM GUI agent autonomously operates a mobile device by iterating a perception--reasoning--action
loop: it captures a screenshot, passes it to a vision-language model, receives an action
(tap, swipe, type, scroll), and dispatches that action to the device~\cite{appagent2024,autoglm2024}.%
On Android, two injection pathways are available without root access.%
\textit{ADB shell input}: \texttt{adb shell input tap X Y} synthesizes a \texttt{MotionEvent}
and injects it directly into the Android input dispatch pipeline via \texttt{InputFlinger}.%
\textit{AccessibilityService}: \texttt{dispatchGesture()} constructs a
\texttt{GestureDescription} object and delivers it through the Android accessibility subsystem.%
Both pathways generate software \texttt{InputEvent} objects; neither triggers any hardware
actuation of the capacitive touchscreen.%

LLM agents are openly available and economically viable as fraud infrastructure.%
AutoGLM~\cite{autoglm2024} achieves 36.2\% success rate on general phone tasks and is
commercially deployed; AppAgent~\cite{appagent2024} reached a 50\% task-completion rate
on a 50-task Android benchmark.%
Documented fraud use cases include mass account creation, advertising click fraud,
welfare and bonus farming, and silent payment confirmation during remote-assistance scams.%
Unlike scripted bots that repeat fixed sequences, LLM agents adapt to UI state changes,
making trajectory-level detection significantly harder.%

\subsection{Kinematic Detection and Its Limitation}
\label{sec:bg_kinematic}

Turing Test on Screen~\cite{ttos2026} established that vanilla LLM agents are detectable
via touch kinematic anomalies: coordinates cluster near UI element centers, velocity
profiles lack the smooth deceleration of human finger approach, and timing lacks
neuromotor jitter.%
BeCAPTCHA~\cite{becaptcha2021} earlier demonstrated that accelerometer and touchscreen
features combined can separate scripted bots from humans.%

The fundamental weakness of kinematic detection is that it measures \textit{learned
behavioral statistics}: an LLM agent equipped with a human-motion synthesis
model~\cite{swipegen2025} can generate touch events whose kinematics are
statistically indistinguishable from real users.%
Indeed, Turing Test on Screen trains a ``humanization'' pipeline against its own detector,
showing that kinematic defense and offense are engaged in an arms race with no
physics-grounded endpoint.%
Turing Test on Screen explicitly delineates physical sensor spoofing---making the
accelerometer signal consistent with a human-held phone---as a challenge that requires
``significant technical effort'' and lies outside its scope.%
Our work addresses exactly this open problem.%

\subsection{Physical Causality of Real Touch}
\label{sec:bg_causality}

When a human finger contacts a capacitive touchscreen, the mechanical impact transmits
an impulse through the phone chassis via Newton's third law.%
The impulse excites the MEMS accelerometer element: a brief ($\lesssim$100\,ms) acceleration
transient is superimposed on the device's background motion~\cite{biomotouch2026}.%
This causal chain---\textit{finger contact} $\rightarrow$ \textit{mechanical impulse}
$\rightarrow$ \textit{accelerometer transient}---is a physical necessity; it occurs
regardless of the user's grip posture, motion context, or device model.%

ADB and \texttt{AccessibilityService} touch injection never actuate the touchscreen
hardware.%
No physical contact occurs, no impulse propagates through the chassis, and
the accelerometer is unaffected.%
This is not an implementation oversight in LLM agent frameworks; it is a
\textit{structural property of software input injection}: an InputEvent object
dispatched through the Android input pipeline carries no energy and exerts no
mechanical force.%
No software-side modification can change this.%

\subsection{Zero-Permission Accelerometer}
\label{sec:bg_sensor}

Android's \texttt{TYPE\_LINEAR\_ACCELERATION} composite sensor reports the
device acceleration with gravity removed, requiring no declared permission.%
It is available on virtually all Android devices since API level~9 and remains
accessible to background apps without the \texttt{HIGH\_SAMPLING\_RATE\_SENSORS}
permission at the default \texttt{SENSOR\_DELAY\_FASTEST} rate
($\approx$200\,Hz on current hardware; up to 400\,Hz on flagship models).%
No sensitive-data permission, no user-visible prompt, and no Play Store policy
restriction applies to its use.%
The impulse response of real touch is detectable at this sampling rate given its
characteristic peak amplitude of $\approx$3.2\,mg and its
sub-60\,ms dominant duration.%
