\section{Conclusion}
\label{sec:conclusion}

LLM GUI agents defeat device attestation and kinematic detection because they run on
real hardware and can synthesize statistically plausible touch trajectories.%
The distinguishing property of an agent-controlled session is not its behavioral
statistics but its \textit{physical origin}: software touch injection never actuates
the touchscreen hardware, so no mechanical impulse propagates through the chassis
and no accelerometer transient is produced.%

PhysCausal exploits this structural impossibility via the zero-permission linear
accelerometer.%
The Physical Causality Consistency Network introduces three physics-informed components:
PC-CWA, which embeds a hard causal window mask and a learnable exponential decay prior
directly into the cross-modal attention mechanism; ISPM, which performs frequency-domain
prototype matching to discriminate broadband finger impulses from narrowband motor
oscillation and agent noise floor; and a differentiable PCS layer that produces
per-event causal attribution without post-hoc analysis.%
An Overlay-Aware Loss trains the model to localize event-level causality failures
at the server-selected challenge position $t^*$, enabling detection of the novel
overlay agent threat where an LLM agent injects fraudulent actions into a live human session.%

Evaluated on 52 participants across 18 Android device models, PhysCausal achieves
97.3\% accuracy and 1.8\% EER under a zero-overlap device-model split,
with 94.8\% accuracy against A1 vibration motor adversaries and 96.9\% against
A2 timing-mimicry adversaries that reduce kinematic detection to near-chance.%
Attention visualization and prototype analysis confirm that PCCN independently
rediscovers the physical impulse window and the three spectral impulse types,
providing an interpretable and physics-grounded explanation for every detection decision.%

The broader implication is that \textit{physical causality signals} constitute an
unforgeable primitive for mobile session liveness: their presence requires genuine
human contact that no software injection can fabricate, and their targeted absence
at a server-specified challenge time cannot be concealed by any pre-recorded stream.%
Future work includes multi-sensor fusion with the magnetometer (combining accelerometer
impulse causality and EM touch transients~\cite{istelan2023}) when elevated permissions
are available, federated deployment models preserving user privacy while aggregating
detection evidence across installations, and investigation of A3-level physical
tethering countermeasures to bound the economic cost imposed on sophisticated
farm operators.%
