\section{Introduction}
\label{sec:intro}

The emergence of large language model (LLM)-driven mobile GUI agents represents a qualitative
shift in mobile automation fraud.%
Frameworks such as AutoGLM~\cite{autoglm2024}, AppAgent~\cite{appagent2024}, and Anthropic's
Computer Use~\cite{anthropiccu2024} enable a remote operator to direct a smartphone by
supplying natural-language goals: the agent observes the screen, reasons about the next
action, and injects touch events via the Android Debug Bridge (ADB) or
\texttt{AccessibilityService}.%
These systems are openly available, cost under \$0.01 per action, and are already deployed for
account registration fraud, advertising click abuse, bonus farming, and unauthorized payment
initiation~\cite{llmagentfraud2025}.%
At scale, a single operator can simultaneously control thousands of devices, achieving a
human-to-session ratio of 1:1{,}000 or greater---an economic asymmetry that renders
manual review economically infeasible.%
Unlike classical scripted bots that repeat fixed action sequences, LLM agents are adaptive:
they navigate unexpected UI states, solve simple CAPTCHAs, and can be equipped with
human-motion synthesis to mimic plausible touch trajectories~\cite{swipegen2025}.%

\textit{Kinematic detection is insufficient against LLM agents.}%
The state-of-the-art detection approach, represented by Turing Test on Screen~\cite{ttos2026},
analyzes touch kinematic features---coordinates, velocity, inter-touch duration---to distinguish
LLM agents from human operators.%
This framing asks: \textit{does this interaction look like a human?}%
An LLM agent augmented with a motion-synthesis model can answer ``yes'' without requiring
any physical contact: it generates touch events whose coordinate trajectories and timing
distributions match the statistical fingerprint of real users.%
Turing Test on Screen itself acknowledges that \textit{``achieving high-fidelity humanization
of SensorEvents poses significant technical challenges''} and delineates physical sensor
spoofing as an open problem outside its scope.%
BeCAPTCHA~\cite{becaptcha2021}, a precursor using accelerometer and touchscreen biometrics,
was designed for fixed-script bots predating the LLM agent era and is similarly circumventable
by realistic motion synthesis.%
This kinematic arms race has no physics-grounded endpoint.%

We observe that the right question is not ``does this interaction \textit{look} like a
human?''\ but rather ``did this interaction \textit{physically originate} from a human?''%
Every real finger contact with a smartphone touchscreen initiates a chain of physical
events that are fundamentally inaccessible to software automation.%
The mechanical impulse of a fingertip striking the glass propagates through the phone chassis
and produces a measurable acceleration transient at the MEMS accelerometer---a brief,
sub-100\,ms broadband pulse detectable by the \textit{zero-permission} linear accelerometer
(\texttt{TYPE\_LINEAR\_ACCELERATION})~\cite{androidSensor}.%
ADB-injected and \texttt{AccessibilityService}-dispatched touch events are software
\texttt{InputEvent} objects; they traverse the Android input dispatch pipeline but never
actuate the touchscreen hardware.%
No finger makes contact, no impulse propagates, and the accelerometer remains silent.%
This \textit{physical causality gap} is a structural impossibility for software automation---
unlike kinematic statistics, it cannot be forged by any combination of timing adjustments
or synthetic trajectory generation.%

We present \textit{PhysCausal}, a challenge-response system that exploits the physical
causality gap to detect LLM GUI agents using only the zero-permission accelerometer.%
PhysCausal operates in two complementary modes.%
In \textit{passive mode}, the system continuously correlates the touch-event timestamp stream
$\tau(t)$ against the linear acceleration signal $\delta(t)$: for each reported touch, it
checks whether an accelerometer impulse is present in the subsequent $[0,\,80]$\,ms window.%
In \textit{active mode}, the server additionally selects a random challenge time
$t^* \in [\frac{T}{4},\frac{3T}{4}]$ after recording begins, prompting a single tap;
the physical impulse at $t^*$ is then verified.%
Because $t^*$ is chosen after the session starts, pre-recorded impulse streams cannot
contain a correctly timed transient.%

The core classification model, the \textit{Physical Causality Consistency Network} (PCCN),
is purpose-built around the physics of the problem.%
Three design innovations differentiate PCCN from generic cross-modal architectures.%
First, \textit{Physics-Constrained Causal Window Attention} (PC-CWA) replaces generic
cross-modal attention with a hard causal mask that restricts attention to the
physically meaningful window $[0, T_{\mathrm{win}}]$ after each touch, augmented by a
learnable exponential decay prior that encodes the known impulse response envelope.%
Second, an \textit{Impulse Spectral Prototype Module} (ISPM) maintains a learned bank
of $K$ prototype spectra---representing broadband finger impact, narrowband motor oscillation,
and sensor noise floor---and performs frequency-domain prototype matching within each
causal window, enabling fine-grained classification of the \textit{type} of impulse present.%
Third, a differentiable \textit{Physical Causal Score} (PCS) layer aggregates per-event
attention mass into an explicit $[0,1]$ causal indicator that is used as a model feature,
making causality attribution directly interpretable without post-hoc analysis.%

\textit{Overlay agent detection.}
We introduce a third-class threat not addressed by prior work: the \textit{overlay agent},
in which an LLM agent injects fraudulent actions (e.g., payment confirmation taps)
\textit{on top of} a session where a legitimate user is physically holding the phone.%
This corresponds to the ``authorized push payment'' fraud scenario in which an attacker
remotely controls actions while the victim believes they are the sole operator.%
PCCN detects overlay agents via the active challenge: the injection at $t^*$ leaves no
accelerometer impulse at that specific timestamp, producing a locally low PCS at $t^*$
against a background of high PCS values from genuine human touches.%
An \textit{Overlay-Aware Loss} (OAL) trains the model to localize this event-level
causality failure rather than relying on session-level statistics.%

We evaluate PhysCausal on 52 participants across 18 Android device models
(Pixel, Galaxy, OnePlus, Xiaomi families) as the human class, and three LLM agent
frameworks (AutoGLM, AppAgent, custom ADB scripts) under A0--A2 adversary conditions.%
PCCN achieves 97.3\% accuracy and 1.8\% EER in active mode under a zero-overlap
device-model split, outperforming all baselines including against timing-mimicry (A2)
adversaries that reduce kinematic detection to near-chance.%
Post-hoc attention visualization confirms that PC-CWA independently concentrates on the
$[0,\,60]$\,ms post-touch window, and prototype visualization shows that ISPM recovers
physically interpretable spectral prototypes without any spectral supervision.%

\noindent\textbf{Contributions.}
\begin{itemize}[leftmargin=*,topsep=2pt,itemsep=1pt]
  \item \textbf{Physical causality as a liveness primitive.}
        We identify and formalize the mechanical impulse response of real finger contact as
        a zero-permission, structurally unforgeable signal that software injection cannot
        replicate, closing the gap that kinematic-based detection leaves open.

  \item \textbf{Physics-informed PCCN architecture.}
        We design PC-CWA, embedding physical impulse response priors (causal mask +
        learnable decay) directly into the attention mechanism; ISPM for frequency-domain
        prototype matching across three impulse types; and a differentiable PCS layer
        for interpretable per-event causality attribution---the first architecture to
        encode physical impulse response physics as structural inductive biases.

  \item \textbf{Three-class threat model and overlay agent detection.}
        We define the novel overlay agent threat and propose an Overlay-Aware Loss that
        trains the model to localize event-level causality failures at the server-issued
        $t^*$, achieving 91.3\% detection accuracy from a single challenge event.

  \item \textbf{Cross-device evaluation and physics-grounded interpretability.}
        We demonstrate 97.3\% accuracy under a zero-overlap 18-model device split and show
        that PCCN rediscovers the physical impulse window and recovers interpretable spectral
        prototypes without explicit feature engineering.
\end{itemize}
