\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{microtype}

\begin{document}

\title{PhysCausal: Detecting LLM GUI Agents via the Zero-Permission\\
Physical Causality Gap}

\author{
  \IEEEauthorblockN{Anonymous Author(s)}
  \IEEEauthorblockA{
    \textit{Anonymous Institution}\\
    anonymous@example.com
  }
}

\maketitle

\begin{abstract}
LLM-driven mobile GUI agents inject touch events via ADB or \texttt{AccessibilityService},
bypassing capacitive touchscreen hardware and leaving no mechanical trace in the device
accelerometer.
We identify this as the \textit{physical causality gap}: real finger contact
transmits a broadband impulse ($\lesssim$100\,ms, $\sim$2--5\,mg) detectable by the
\textit{zero-permission} \texttt{TYPE\_LINEAR\_ACCELERATION} sensor, whereas software
injection produces no accelerometer response---a structural impossibility no timing
or trajectory adjustment can overcome.
We present \textit{PhysCausal}, a challenge-response system that exploits this gap.
In \textit{passive mode}, the Physical Causality Consistency Network (PCCN) jointly
processes the accelerometer deviation signal and touch-event timestamps via cross-modal
attention, detecting the presence or absence of causal impulse coupling at each touch.
In \textit{active mode}, a server-selected challenge time $t^*$, communicated only
\textit{after} recording begins, additionally defeats pre-recorded impulse injection and
enables detection of a novel \textit{overlay agent} threat---where an LLM agent injects
fraudulent taps into a live human session.
PCCN is trained via masked accelerometer pre-training, supervised contrastive fine-tuning,
and cross-modal head training.
Evaluated on \textcolor{red}{XX} participants across \textcolor{red}{XX} Android device
models under A0--A2 adversary conditions, PhysCausal achieves \textcolor{red}{>XX\%}
accuracy with \textcolor{red}{<XX\%} EER under a zero-overlap device-model split.
Post-hoc attention visualization confirms that PCCN rediscovers the [0,\,60]\,ms
physical impulse window without explicit supervision.
\end{abstract}

\begin{IEEEkeywords}
LLM GUI agents, mobile fraud detection, physical liveness, accelerometer, cross-modal
attention, challenge-response
\end{IEEEkeywords}

\input{introduction}
\input{background}
\input{PreliminaryAnalysis}
\input{SystemModelAndAdversaryModel}
\input{method}
\input{relatedwork}
\input{experiment}
\input{conclusion}

\bibliographystyle{IEEEtran}
\bibliography{ref}

\end{document}
